### 2020-04-06 discussion.tex
miscellaneous ...

\section{Discussion}
\label{sec:discussion}
\fix{Jim and everyone}

>>>>

\section{Discussion}
\label{sec:discussion}
\fix{Christian, Jim and everyone}

\begin{itemize}
\item Cray and NVIDIA take care of the hardware and some systems and driver
  software so moving and troubleshooting hardware is their cost.
\item Checkpoint strategies, allocation strategies, job resource
  management, are all under OLCF control. What can OLCF do/change to
  mitigate fallout in terms of delivering computing to customers when
  facing machine disasters like the two episodes (2013 and 2016) on Titan?
\end{itemize}
